\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{graphicx}

% ---- Commands ------- %
\newcommand{\documentNumber}[1]{
    \LARGE  \textbf{ PUSS2142{#1} } \\
    \medskip
}
\newcommand{\documentVersion}[1]{
    v.{#1} \\
    \medskip
}
\newcommand{\documentTitle}[1]{
    \centerline{\rule{13cm}{0.4pt}}
    \bigskip \bigskip
    \LARGE {#1} \\
    \bigskip \bigskip
    \centerline{\rule{13cm}{0.4pt}}
}
\newcommand{\documentGroup}[1]{
    \bigskip \bigskip
    \LARGE Group {#1} \\
    \bigskip
}
\newcommand{\documentResponsible}[1]{
    \LARGE Responsible: {#1} \\
    \medskip
}
\newcommand{\documentAuthors}[1]{
    \LARGE Authors: {#1} \\
    \medskip    
}
\newcommand{\documentDate}[1]{
    \date {#1} 
}

\graphicspath{{./images/}} %Defines a path to file images

% --- Header & Footer ---- %
\pagestyle{fancy}
\lhead{\leftmark}
\rhead{}
\rfoot{\thepage}
\cfoot{}
\lfoot{}


% ------------------------------------------------ #

% ----- FILL THIS ----- %
\title {
    % Must be 2 digits
        \documentNumber {10}    
    
    \documentVersion {1}
    
    % Full name - SHORTNAME
    \documentTitle {Informal Review Protocol}
    \documentGroup {2}
    
    % Options: - Project management Group
    %          - System architecture Group
    %          - Developer Group
    %          - Test Group
    \documentResponsible {Project management group}
    \documentAuthors {Project management group}
    
    % Format: YYYY-MM-DD
    \documentDate {2021-01-31}
}

\begin{document}

\maketitle
\thispagestyle{empty}

\newpage

\tableofcontents

\newpage

%---------Document begins here-----------

\section{Introduction}
    The goal of the informal review is to identfiy discrepencies between documents, grammatical errors and ambiguities. A documents does \emph{not} pass an informal review, it is only a system for detecting errors that would cause it to fail a formal review.  
    Since most of the documents that are produced during a phase are dependant on other documents, the informal review covers every docuemnt written during the phase.

\section{Preparation}
    \subsection{Picking reviewers}
        PG is resposible for picking a set of reviewers from the subgroups. Documents should be reviewed by 3 people from a group that has not authored the document. The reviewers are to do their reviews independently. Reviewers should be rotated for an even work distribution.

    \subsection{Submitting a document for review}
        Every group makes sure that an up to date verison of their docuemnt
        available at latest 17:00 the day before the informal review meeting. Should the document be in an unfinished state at this time, authors will make a note covering what parts are unfinished. Unfinished parts of the document will be ignored by reviewers. 

\newpage
\section{Exectuion}
    Documents and code have different criteria and should therefor be reviewed differently. Be sure to take notes whilst reading so that the authors can go over it later. 
    
    \subsection{Document Criteria}
    \begin{itemize}
        \item Is the docuemnt grammatically correct and adheres to the our document standards?
        \item Does the document cover all the necessery points defined in the project tutorial?
        \item If the document is dependant on another document, do the contents of the document match? Meaning, is there any confusion as to how they relate to one and other.
    \end{itemize}
    
    \subsection{Code Criteria}
    \begin{itemize}
        \item Does the code follow the high level architecture defined by the System architecture group?
        \item Does the code adhere to our coding standard?
        \item Do comments follow the javadoc-convention?
        \item Does the software behave as expected?
        \item Is it possible to 'break' the software?
    \end{itemize}
    
    
\newpage
\section{Reporting results and correcting}
    \subsection{Informal Review Meeting}
        The result will be reported in a group-wide meeting. Every document gets 10-20 minutes of time. If the results warrant further discussion, the parties involved will continue the discussion after the meeting.

    \subsection{Correcting Eventual Errors}
        Informal reviews are scheduled to give authors enough time to correct errors before the hand in-deadline for formal reviews.

\end{document}
